### 2021-06-01 sections/experience.tex
Update experience.tex

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, Chile} 
{2013 - 2016}
{School of Government and Public Management, Institute for Public Affairs}\vspace{1.5mm}

>>>>

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, Chile} 
{2013 - 2016}
{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
